### 2015-05-29 ISWAG_PRESENTATION/PRESENTATION_ISWAG.TEX
iswag presentation

	  \fancyhead[L]{\theslideheading}
	  \fancyhead[R]{\textcolor{blue}{\eadsccr \thepage }}
	  \fancyfoot[R]{\textcolor{blue}{}}
	  \fancyfoot[L]{\textcolor{blue}{Deauville, 03 June 2015 }}
	  \renewcommand\headwidth{\textwidth}
	  \autoslidemarginstrue

@@

	  \slideframe{none}
	  %\XgrDefinitFormat{*}{line=0,mark=0,ll=1}
	  %\XgrDefinitFormat{pr}{}
	  %\XgrDefinitFormat{ks}{line=-1,mark=8,ll=0.4}
	  \begin{document}
	  \slidepagestyle{fancy}
	  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	  \begin{slide}
	  \thispagestyle{plain}
	  \begin{center}
	  \textcolor{blue}{\huge Internal mesh optimization}\\
	  \textcolor{blue}{\huge Semantic linking and siloing}\\
	  \textcolor{blue}{\huge Big data}\\
	  \vspace{0.25 cm}
	  \textbf{DUPREY Stéfan}\\
	  \small{\textbf{Cdiscount}\\

	  }
	  %\eadsccr
	  \end{center}
	  \end{slide}
	  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	  {\small{
	  \begin{slide}
	  \slidecontents
	  \renewcommand\theslideheading{Plan}
	  \end{slide}
	  \begin{slide}
	  \slideheading{Introduction}
	  \textbf{\textcolor{blue}{\large Objective : give you an overview of the meshing optimization done at Cdiscount, the first french e-commerce web site }}
	  \small{
	  \newline $\bullet$ Heuristic based optimization algorithm to push specific products 
	  \newline $\bullet$ An e-commerce pitch
	  \newline $\bullet$ Semantic similarity and constraining for shrinking our universe
	  \newline $\bullet$ Big data implementation
	  }
	  \end{slide}
	  \begin{slide}
	  \slideheading{Heuristic}
	  \textbf{\textcolor{blue}{\large Some notations}}\newline
	  Let $N\in\mathbb{N}$ be the number of nodes in our mesh.
	  \newline
	  Let $\left(X_i\right)_{i \in \left\{1,...,N\right\}}$ be the vertices (URLs) of our oriented graph.
	  \newline
	  Let $\left(G_{ij}\right)  \in \left\{0,1\right\}^{N\times N}$ be the adjacency matrix of our oriented graph.
	  \newline
	  Let here define f, a given data per URL, which gives a potentiality metrics for our vertices.
	  \begin{equation}
	  \begin{array}{ccccc}
	  f & : & \left(X_i\right)_{i \in \left\{1,...,N\right\}} & \to & \mathbb{R}^{+} \\
	  & & x & \mapsto & f(x) \\
	  \end{array}
	  \end{equation}
	  \end{slide}
	  \begin{slide}
	  \textbf{\textcolor{blue}{\large In-rank}}\newline      
	  We restrain the universe to our site where we compute the standard page-rank.
	  \newline
	  Initialization :
	  \begin{equation}
	  \forall u \ PR\left(u\right)=\frac{1}{N}
	  \end{equation} 
	  Iterative computation :
	  \begin{equation}
	  PR\left(u\right)= \frac{\left(1-c\right)}{N} + c \times \sum_{v \rightarrow u}\frac{PR\left(v\right)}{card\left(\left\{v\rightarrow u\right\}\right)}
	  \end{equation}
	  \end{slide}
	  \begin{slide}
	  \textbf{\textcolor{blue}{\large Our heuristic}}\newline 
	  We want here to optimize the adequacy of our mesh $\left(X_i\right)$ to our potentiality vector $f$.
	  We here postulate the following heuristic to assess the relevance of a mesh :
	  \begin{equation}
	  \max_{\left(G_{ij}\right)  \in \left\{0,1\right\}^{N\times N}}\left\{ \sum^{N}_{i=1} trafic\left(X_i\right)\times pageRank(X_i)\right\}
	  \end{equation} 
	  \end{slide}

@@

	  \textbf{\textcolor{black}{\large What a genetic algorithm}}

@@

	  \newline \textbf{\textcolor{black}{\large Why a genetic algorithm}}

@@

	    $$
    \left(X_i\right)=\{'home','metalist1','metalist2',
    $$
    $$
    'list1','list2','list3','list4',
    $$
    $$
    'product1','product2',...,'product32'\};
    $$
    $$
    f\left(X_i\right) = [100;80;55;$$
    $$
    40;35;25;20;
    $$
    $$
    4;5;...;3]
    $$

@@

    \textbf{\large Initial population}

@@

    \epsfig{file=initial_population.eps,height=5cm,width=5cm}
    \textbf{\large Population at convergence}
    \epsfig{file=converged_population.eps,height=5cm,width=5cm}
    \textbf{\large Best chromosome fitness function evolution}
    \epsfig{file=best_element_evolution.eps,height=5cm,width=5cm}
    The structure found is as we expected arborescent : home linking to metalists, metalists linking to lists and lists to products.
    \textbf{\large Optimal site structure}
    \epsfig{file=site_structure.eps,height=5cm,width=5cm}

@@

	    \epsfig{file=neo4j_maze_runner.eps,height=3cm,width=8cm}

@@

>>>>

	    \fancyhead[L]{\theslideheading}
	    \fancyhead[R]{\textcolor{blue}{\eadsccr \thepage }}
	    \fancyfoot[R]{\textcolor{blue}{}}
	    \fancyfoot[L]{\textcolor{blue}{ISWAG Deauville, 3 June 2015 }}
	    \renewcommand\headwidth{\textwidth}
	    \autoslidemarginstrue

@@

	    \slideframe{none}
	    %\XgrDefinitFormat{*}{line=0,mark=0,ll=1}
	    %\XgrDefinitFormat{pr}{}
	    %\XgrDefinitFormat{ks}{line=-1,mark=8,ll=0.4}
	    \begin{document}
	    \slidepagestyle{fancy}
	    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	    \begin{slide}
	    \thispagestyle{plain}
	    \begin{center}
	    \textcolor{blue}{\huge Internal mesh optimization}\\
	    \textcolor{blue}{\huge Semantic linking and siloing}\\
	    \textcolor{blue}{\huge Big data}\\
	    \vspace{0.25 cm}
	    \textbf{DUPREY Stefan}\\
	    \small{\textbf{Cdiscount}\\

	    }
	    %\eadsccr
	    \end{center}
	    \end{slide}
	    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	    {\small{
	    \begin{slide}
	    \slidecontents
	    \renewcommand\theslideheading{Plan}
	    \end{slide}
%	    \begin{slide}
%	    \slideheading{Introduction}
%	    \textbf{\textcolor{blue}{\large Objective : give you an overview of the meshing optimization done at Cdiscount, the first french e-commerce web site }}
%	    \small{
%	    \newline $\bullet$ Heuristic based optimization algorithm to push specific products 
%	    \newline $\bullet$ An e-commerce pitch
%	    \newline $\bullet$ Semantic similarity and constraining for shrinking our universe
%	    \newline $\bullet$ Big data implementation
%	    }
%	    \end{slide}
	    \begin{slide}
	    \slideheading{Heuristic}
	    \textbf{\textcolor{blue}{\large Some notations}}\newline
	    Let $N\in\mathbb{N}$ be the number of nodes in our mesh.
	    \newline
	    Let $\left(X_i\right)_{i \in \left\{1,...,N\right\}}$ be the vertices (URLs) of our oriented graph.
	    \newline
	    Let $\left(G_{ij}\right)  \in \left\{0,1\right\}^{N\times N}$ be the adjacency matrix of our oriented graph.
	    \newline
	    Let here define f, a given data per URL, which gives a potentiality metrics for our vertices.
	    \begin{equation}
	    \begin{array}{ccccc}
	    f & : & \left(X_i\right)_{i \in \left\{1,...,N\right\}} & \to & \mathbb{R}^{+} \\
	    & & x & \mapsto & f(x) \\
	    \end{array}
	    \end{equation}
	    \end{slide}
	    \begin{slide}
	    \textbf{\textcolor{blue}{\large In-rank}}\newline      
	    We restrain the universe to our site where we compute the standard page-rank.
	    \newline
	    Initialization :
	    \begin{equation}
	    \forall u \ PR\left(u\right)=\frac{1}{N}
	    \end{equation} 
	    Iterative computation :
	    \begin{equation}
	    PR\left(u\right)= \frac{\left(1-c\right)}{N} + c \times \sum_{v \rightarrow u}\frac{PR\left(v\right)}{card\left(\left\{v\rightarrow u\right\}\right)}
	    \end{equation}
	    \end{slide}
	    \begin{slide}
	    \textbf{\textcolor{blue}{\large Our heuristic}}\newline 
	    We want here to optimize the adequacy of our mesh $\left(X_i\right)$ to our potentiality vector $f$.
	    We here postulate the following heuristic to assess the relevance of a mesh :
	    \begin{equation}
	    \max_{\left(G_{ij}\right)  \in \left\{0,1\right\}^{N\times N}}\left\{ \sum^{N}_{i=1} trafic\left(X_i\right)\times pageRank(X_i)\right\}
	    \end{equation} 
	    \end{slide}

@@

	    \textbf{\textcolor{black}{\normalsize What is a genetic algorithm}}

@@

	    \newline \textbf{\textcolor{black}{\normalsize Why a genetic algorithm}}

@@

	    {\scriptsize{
	      $\left(X_i\right)$ ={'home','metalist1','metalist2','list1','list2','list3','list4','product1','product2',...,'product32'};
              $f\left(X_i\right)$=[   100,         80,         55,     40,     35,     25,     20,         4,         5,...,3          ];
	    }}

@@

      \textbf{\large Results}

@@

      \epsfig{file=prototyping_example.eps,height=5.cm,width=5.cm}

@@

	      \epsfig{file=neo4j_maze_runner.eps,height=3.cm,width=12.cm}

@@

	     \slideheading{Video and paper link}
        	    \textbf{\textcolor{blue}{\normalsize http://sduprey.github.io/page\_rank\_optimization\_video.html}}\newline 
        	    \textbf{\textcolor{blue}{\normalsize http://sduprey.github.io/article\_sduprey\_iswag\_02\_06\_2015.pdf}}\newline 
       	            \textbf{\textcolor{blue}{\normalsize http://sduprey.github.io/PRESENTATION\_ISWAG.pdf}}\newline 
